### 2014-03-15 src/methodology.Rnw
Switching off Amins comment
Adding n-selective criteria

{\bf Amin: The rest of this section is for Alex and Carlos info and should be verified if we should include this or wave our hands about approximation instead.}

\subsubsection{Criteria I}
For this criteria, we used the two operators \pitcb, and \pitnc which are similar to those given by Wong. We did not have ABS operator available in PIT.
\subsubsection{Criteria II}
We used the operators given by Offutt et al. \pitin, \pitm, \pitcb, \pitnc. We did not have LCR available in PIT.
\subsubsection{Criteria III}
Those given by Javalanche \pitnc, \pitvmc, \pitnvmc, \pitm, \pitic, \pitemv. 
\subsubsection{Criteria IV}
By Namin et al. \pitin, \pitm, \piti, \pitnc. Many of operators were not applicable in Java and some were not available in PIT like IndVarBitNeg.

>>>>

% {\bf Amin: The rest of this section is for Alex and Carlos info and should be verified if we should include this or wave our hands about approximation instead.}

\subsubsection{Criteria I}
For this criteria, we used the two operators \pitcb, and \pitnc which are similar to those given by Wong. We did not have ABS operator available in PIT.
\subsubsection{Criteria II}
We used the operators given by Offutt et al. \pitin, \pitm, \pitcb, \pitnc. We did not have LCR available in PIT.
\subsubsection{Criteria III}
Those given by Javalanche \pitnc, \pitvmc, \pitnvmc, \pitm, \pitic, \pitemv. 
\subsubsection{Criteria IV}
By Namin et al. \pitin, \pitm, \piti, \pitnc. Many of operators were not applicable in Java and some were not available in PIT like IndVarBitNeg.
\subsubsection{Criteria V}
For this criteria, we utilized the approach suggested by
Offutt et al.~\cite{offutt1993experimental} where by most numerous operators
are discarded at each step.
